\speculake: Hiding Malware in Speculative Execution

### 2018-05-02 paper/implementation.tex

\subsection{AES Decryption}

% implementation 
%   Key Schedule expansion / obfuscation
%
% you can speculatively execute AES instructions

>>>>

\subsection{AES Decryption}
The speculative world is able to take advantage of the AES-NI instructions to
decrypt messages. In order to avoid detection (as well as reduce the computation
that needs to be done in the speculative world) the key expansion can be done
ahead of time. However, the key schedule does have a structure that could be
detected by a reverse engineer. Thus 11 random round keys are selected. This
obfuscated key schedule makes it more difficult for a reverse engineer to
determine that there is encrypted content. Additionally since the content is
only accessed when the correct trigger program is running the challenges facing
a reverse engineer are great.
% implementation 
%   Key Schedule expansion / obfuscation
%
% you can speculatively execute AES instructions

### 2018-05-02 paper/payloads.tex

\subsection{Turing Machine}
\label{subsec:turing}
To demonstrate that arbitrary computation can be done in the speculative world
we create a Turing Machine to compute a 6 state Busy Beaver Turing Machine.

@@

To accomodate both developers as well as the unique constraints 
enforced by the speculative primitive, a custom emulation solution is required. We 
have approached this challenge from both directions. First we demonstrate 
general purpose emulation using a custom instruction set -- SPASM -- which
accomodates the speculative primitive specifically. Next we investigate custom 
wrappers on traditional emulators allow for similar payload construction,
with a much more developer friendly

>>>>

\subsection{Turing Machine}
\label{subsec:turing}
To demonstrate that arbitrary computation can be done in the speculative world
we create a Turing Machine to compute a 5 state Busy Beaver Turing Machine. The
Busy Beaver game is tasked with creating a Turing Machine which writes the most
1s on the tape with only a limited number of states and still halts.

The computation of the Turing Machine is done speculatively, meaning that while
the real world keeps track of the state, tape, and symbols of the turing machine
all logic used to update the above is done in the speculative world.

@@

To accommodate both developers as well as the unique constraints 
enforced by the speculative primitive, a custom emulation solution is required. We 
have approached this challenge from both directions. First we demonstrate 
general purpose emulation using a custom instruction set -- SPASM -- which
accommodates the speculative primitive specifically. Next we investigate custom 
wrappers on traditional emulators allow for similar payload construction,
with a much more developer friendly
